Making Sequential Programs Deterministic

### 2019-03-31 related.tex
Notes about related work
Fix typo
Todo notes

>>>>

The state of the art is NonDex.  It is a highly effective tool.

% https://github.com/TestingResearchIllinois/NonDex/wiki/Supported-APIs
NonDex uses a hand-crafted list of 47 methods (25 unique method names) in
in 13 classes.
This is analogous to our annotations on the JDK\@.
\todo{Say how much code our annotations cover?}
\todo{Check whether our JDK is missing anything they support.}
\todo{Did the NonDex authors contact the maintainers of the tools in which
  they found nondeterminism?}
